### 2018-08-30 TeX/organigram1.tex
changed TiX picture

		\node (io) [io, align = center] at (0cm,0cm) {.csv or .xlsx \\ CAS \\ Compound name};
		%% chemicals
		% id nodes

		\node (cas) [ids, below of=io, yshift = -4cm] {CAS};

		% main nodes
		\node (chemprop) [main, dashed, right of=cas, xshift=4.5cm, yshift=3cm] {CHEMPROP};
		\node (epa) [main, ultra thick, right of=cas, yshift=1cm, xshift=4.5cm] {EPA ECOTOX}
			child { node { qu\_epa.R} };
		\node (chemscr) [main, right of=cas, yshift=-1cm, xshift=4.5cm] {PHYS-CHEM}
			child { node { Alan Wood Pesticide Compendium - \textbf{qu\_aw.R } }}
			child { node { Pesticide Action Network - \textbf{ch\_pan.R} }}
			child { node { PhysProp - \textbf{ch\_pp.R} }}
			child { node { PubChem - \textbf{qu\_pubchem.R} }};

@@

		%% final result
		\begin{pgfonlayer}{bg3}
			\node[rectangle, draw, rounded corners, minimum height = 2cm, minimum width = 7cm, fill = gray!10] (appbox) at (20.5cm,-10cm) {};
		\end{pgfonlayer}
		\node (apptext) [above of = appbox, yshift = 0.25cm, xshift = -3cm] {Etox-Base Function}; 
		\node (testres) [res, right of = cas, xshift = 14cm, yshift = -5cm] {Result};
		\node (filtres) [res, right of = testres, xshift = 2cm] {Filter};
		\node (aggres) [res, right of = filtres, xshift = 2cm] {Aggregate};

		%%% arrows %%%
		\begin{pgfonlayer}{bg1}
		\draw [arrow, black] (io) -- (cas);
		\draw [arrow, dashed] (cas.east) -- (chemprop.west);
		\draw [arrow] (cas.east) -- (chemscr.west);
		\draw [arrow] (cas.east) -- (epa.west);

		\draw [arrow] (epa.east) -| (testres.north);
		\draw [arrow] (chemscr.east) -| (testres.north);

		%\begin{scope}[on background layer]
		\begin{pgfonlayer}{bg2}
			\draw [arrow, black] (epa) .. controls (3cm,-8cm) .. (taxon.north);
		\end{pgfonlayer}
		%\end{scope}

>>>>

	\node (io) [io, align = center] at (0cm,0cm) {EPA ECOTOX\\data base};
	%% chemicals
	% id nodes

	\node (cas) [ids, below of=io, yshift = -4cm, xshift = 3cm] {CAS};

	% main nodes
	\node (chemprop) [main, dashed, right of=cas, xshift=4.5cm, yshift=1.5cm] {CHEMPROP};
	\node (chemscr) [main, right of=cas, yshift=-1cm, xshift=4.5cm] {PHYS-CHEM}
	child { node { Alan Wood Pesticide Compendium - \textbf{qu\_aw.R } }}
	child { node { Pesticide Action Network - \textbf{ch\_pan.R} }}
	child { node { PhysProp - \textbf{ch\_pp.R} }}
	child { node { PubChem - \textbf{qu\_pubchem.R} }};

@@

	%% final result
	\node (testres) [res, right of = cas, xshift = 14cm, yshift = -5cm] {Result};
	\node (filtres) [res, right of = testres, xshift = 2cm] {Filter};
	\node (aggres) [res, right of = filtres, xshift = 2cm] {Aggregate};

	\begin{pgfonlayer}{bg3}
	\node[rectangle, draw, rounded corners, minimum height = 2cm, minimum width = 7cm, fill = gray!10, right of = testres, xshift = 1.5cm] (appbox) {};
	\end{pgfonlayer}

	\node (apptext) [above of = appbox, yshift = 0.25cm, xshift = -3cm] {Etox-Base Function};

	%%% arrows %%%
	\begin{pgfonlayer}{bg1}
	\draw [arrow, black] (io) |- (cas.west);
	\draw [arrow, dashed] (cas.east) -- (chemprop.west);
	\draw [arrow] (cas.east) -- (chemscr.west);
	\draw [arrow] (chemscr.east) -| (testres.north);

	\draw [arrow, black] (io) |- (taxon.west);
